---
title: "W241 Final Project Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the raw data

```{r}
library(data.table)
d <- fread('./w241_survey_responses.csv')
head(d)
```

# Remove unnecessary columns
```{r}
colnames(d)

not.needed <- c("StartDate", "EndDate", "Status", "IPAddress", "Progress", "Duration (in seconds)", 
                "Finished", "RecordedDate", "ResponseId", "RecipientLastName", "RecipientFirstName", "RecipientEmail", 
                "ExternalReference", "LocationLatitude", "LocationLongitude", "DistributionChannel", "UserLanguage", 
                "Q3_First Click", "Q3_Last Click", "Q3_Page Submit", "Q3_Click Count", 
                "Q34_First Click", "Q34_Last Click", "Q34_Page Submit", "Q34_Click Count", 
                "Q37_First Click", "Q37_Last Click", "Q37_Page Submit", "Q37_Click Count", 
                "Q12_First Click", "Q12_Last Click", "Q12_Page Submit", "Q12_Click Count", 
                "Q16_First Click", "Q16_Last Click", "Q16_Page Submit", "Q16_Click Count", 
                "Q19_First Click", "Q19_Last Click", "Q19_Page Submit", "Q19_Click Count", "MTurkCode", "Q32")
d[, (not.needed) := NULL]
```

# Rename columns to be more descriptive
```{r}
q.names <- c("gender", "state", "education", "served_military", 
             'weather', 'terrorists', 'marines', 'video_topic_check', 
             'us_involved', 'us_send_aid', 'us_send_troops', 
             'raise_tax_rate', 'join_armed_forces')

setnames(d, q.names)
```

# Convert weather, terrorists and marines to dummy variables
# Treat non-compliers as compliers
```{r}
# Replace NA with 0
# NA means that the subject did not see the video in question
d[is.na(weather), weather := 0]
d[is.na(terrorists), terrorists := 0]
d[is.na(marines), marines := 0]
```

# Get a descriptive summary of data

```{r}
library(psych)

for (q.n in (q.names)) {
  hist(d[, get(q.n)], xlab = (q.n), freq = FALSE )
}
```
# Check how many subjects selected the wrong video topic
# And drop their responses from the data
```{r}
# Topic choices: 
# 1. marines
# 2. weather
# 3. nfl draft
# 4. terrorists
# 5. scott foster 

sum(d$video_topic_check == 3)
sum(d$video_topic_check == 5)

d <- d[video_topic_check %in% c(1, 2, 4)]
```

# Treat non-compliers as compliers
```{r}
# 1 subject said that they did not watch the marines video.
# 1 subject said that they did not watch the terrorists video.
# We will count both of them as treatment compliers.

d[weather == 2, weather := 1]
d[terrorists == 2, terrorists := 1]
d[marines == 2, marines := 1]

sum(d$weather) # 78 
sum(d$terrorists) # 96
sum(d$marines) # 97

```

# Convert gender, state, served_military to factors (aka. dummy variables)
```{r}
d$gender <- as.factor(d$gender)
d$state <- as.factor(d$state)
d$served_military <- as.factor(d$served_military)
```

# Multivariate regression
```{r}
deps <- c('us_involved', 'us_send_aid', 'us_send_troops', 
            'raise_tax_rate', 'join_armed_forces')
indeps <- c("gender", "state", "education", "served_military")
treats <- c('weather', 'terrorists', 'marines', 'treats')

m <- lm( cbind(us_involved, us_send_aid, us_send_troops, raise_tax_rate, join_armed_forces) ~ terrorists + marines, data = d)

# library(mvinfluence)

# influence(m, TRUE, 1)

```

# Create a column of treatments
```{r}
d$treatment <- ifelse(d$weather == 1, 0, 0)
d$treatment <- ifelse(d$terrorists == 1, 1, d$treatment)
d$treatment <- ifelse(d$marines == 1, 2, d$treatment)
# d$treatment <- factor(d$treatment)
```

# Randomization Inference
```{r}

deps <- c('us_involved', 'us_send_aid', 'us_send_troops', 
            'raise_tax_rate', 'join_armed_forces')
indeps <- c("gender", "state", "education", "served_military")
treats <- c('weather', 'terrorists', 'marines', 'treats')

df <- data.frame(d)
df[, deps] <- 6 - df[, deps]
df

weather.means <- apply(df[df$treatment == 0, deps], 2, mean)
terrorists.means <- apply(df[df$treatment == 1, deps], 2, mean)
marines.means <- apply(df[df$treatment == 2, deps], 2, mean)

deps.means <- data.frame(weather.means, terrorists.means, marines.means)
deps.means$TminusW <- deps.means$terrorists.means - deps.means$weather.means
deps.means$MminusW <- deps.means$marines.means - deps.means$weather.means
deps.means$TminusM <- deps.means$terrorists.means - deps.means$marines.means
deps.means

RandomInference <- function(vec, ate, n.trials) {
  set.seed(1234)
  rands <- replicate(n.trials, sample(c(TRUE, FALSE), length(vec), replace = TRUE))

  treats <- apply(rands, 2, FUN = function(x) {return(mean(vec[x]))})
  controls <- apply(rands, 2, FUN = function(x) {return(mean(vec[!x]))})
  rand.ate <- treats - controls
  p <- sum(rand.ate > ate) / length(rand.ate)
  std.err <- sd(rand.ate) / sqrt(length(rand.ate))
  low.bound <- ate - 1.96 * std.err
  high.bound <- ate + 1.96 * std.err
  
  
  return(c(ate, std.err, p, low.bound, high.bound))
}
```

# us_involved
```{r}
print("us_involved")

n.t = 10000

m.ate <- deps.means$TminusW[1] 
res <- RandomInference(df$us_involved, m.ate, n.t)
cat('Terror vs. Weather: ate:', res[1], '(', res[2], ')', 'p-value: ', res[3], 'ci: ', res[4], res[5], '\n')

m.ate <- deps.means$MminusW[1]
res <- RandomInference(df$us_involved, m.ate, n.t)
cat('Marines vs. Weather: ate:', res[1], '(', res[2], ')', 'p-value: ', res[3], 'ci: ', res[4], res[5], '\n')


m.ate <- deps.means$TminusM[1]
res <- RandomInference(df$us_involved, m.ate, n.t)
cat('Terror vs. Marines: ate:', res[1], '(', res[2], ')', 'p-value: ', res[3], 'ci: ', res[4], res[5], '\n')

```
# All with correction for multiple comparisons
```{r}
deps <- c('us_involved', 'us_send_aid', 'us_send_troops', 
            'raise_tax_rate', 'join_armed_forces')
n.t = 10000

EmbellishP <- function(p.val) {
    if(p.val*15 <= 0.01) {
    return(paste0(p.val, '**'))
    }
  
  if(p.val*15 <= 0.05) {
    return(paste0(p.val, '*'))
  } 
  
  return(p.val)
}

for (row.name in deps) {
  deps.sub <- deps.means[deps.means$id == row.name,]
  
  cat('######### ', row.name, ' ###########', '\n')
  m.ate <- deps.sub[deps.sub$id == row.name, 'TminusW']
  res <- RandomInference(df$us_involved, m.ate, n.t)
  p <- EmbellishP(res[3])
  cat(row.name, ': Terror vs. Weather: ate:', res[1], paste0('(', res[2], ')'), 'p-value: ', p, 'ci: ', res[4], res[5], '\n')
  
  m.ate <- deps.sub[deps.sub$id == row.name, 'MminusW']
  res <- RandomInference(df$us_involved, m.ate, n.t)
  p <- EmbellishP(res[3])
  cat(row.name, ': Marines vs. Weather: ate:', res[1], paste0('(', res[2], ')'), 'p-value: ', p, 'ci: ', res[4], res[5], '\n')
  
  m.ate <- deps.sub[deps.sub$id == row.name, 'TminusM']
  res <- RandomInference(df$us_involved, m.ate, n.t)
  p <- EmbellishP(res[3])
  cat(row.name, ': Terror vs. Marines: ate:', res[1], paste0('(', res[2], ')'), 'p-value: ', p, 'ci: ', res[4], res[5], '\n')
  
  cat('####################################\n\n')
}

```

# Results

**After correcting for multiple comparisons i.e. 3 treatments x 5 dependent variables, we see that only the following results are significant.**

1. **us_send_aid (placebo value 3.410256)** : Marines vs. Weather: ate: 0.5175786 (0.00135190409440195) p-value:  1e-04** ci:  0.5149289 0.5202284. For sending aid, the average effect was to move the sample from being inbetween "Neither in favor nor opposed" to "Somewhat in favor".


2. **join_armed_forces (placebo value 1.923077)** : Marines vs. Weather: ate: 0.5717684 (0.00135190409440195) p-value:  0** ci:  0.5691187 0.5744182. For joining the armed forces, the average effect was to move the sample from "Somewhat opposed" to "Neither in favor nor opposed".

**That is, subjects who saw the marines video were likely to increase their support for sending Aid to countries fighting terrorists, and joining armed forces, by approx. half a category.**


# MANOVA
```{r}
library(car)
m <- lm( cbind(us_involved, us_send_aid, us_send_troops, raise_tax_rate, join_armed_forces) ~ terrorists + marines, data = df)
summary(m)
summary(Anova(m))

```


